---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r message=FALSE, warning=FALSE, results='hide'}
library(tibble)
library(lubridate)
library(dplyr)
```

```{r}
temp<-read.csv("repdata_data_activity/activity.csv",header=TRUE)
temp<-transform(temp,date=as.Date(date))
activityData<-tibble::as_tibble(temp)
head(activityData)
```



## What is mean total number of steps taken per day?
We'll first group and count total number of step done each day then report mean and median

```{r message=FALSE, warning=FALSE, results='hide'}
sumofSteps<-tapply(activityData$steps,activityData$date,sum,na.rm=TRUE)
meanstep<-mean(sumofSteps)
mediansteps<-median(sumofSteps)
print("mean of steps:")
print(meanstep)
print("median of steps:")
print(mediansteps)
```

```{r echo=FALSE}
print("mean of steps:")
print(meanstep)
print("median of steps:")
print(mediansteps)
```

now we'll plot using base histogram

```{r echo=FALSE}
hist(sumofSteps,xlab="sum of steps taken per day",main = "TOTAL STEPS")
```

## What is the average daily activity pattern?
for this we gonna need ggplot2 
```{r message=FALSE, warning=FALSE}
library(ggplot2)
```

we aggregate data to make correct plot 
```{r}
intr_avg<-activityData %>% 
    group_by(interval) %>% 
    mutate(avg=mean(steps,na.rm=TRUE))
```

we now find which interval has max avg
```{r}
intr_avg[which.max(intr_avg$avg),]
```

and now the plot 
```{r}
qplot(intr_avg$interval,intr_avg$avg,geom="line",
      xlab="interval",
      ylab="avergae",
      main="average steps per interval 5-min")

```

## Imputing missing values
Reporting missing value
```{r}
missing<-is.na(activityData$steps)
table(missing)
```

we can fill missing value by avg of interval that day

```{r}
replacewithmean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
activityDataNa<-activityData %>% group_by(interval) %>% mutate(steps= replacewithmean(steps)) 

```

Calculating and report mean again 
```{r results='hide'}
sumofStepsNA<-tapply(activityDataNa$steps,activityDataNa$date,sum)
meanstep<-mean(sumofStepsNA)
mediansteps<-median(sumofStepsNA)
print("mean of steps:")
print(meanstep)
print("median of steps:")
print(mediansteps)
```

```{r echo=FALSE}
print("mean of steps without na:")
print(meanstep)
print("median of steps without na:")
print(mediansteps)
```

now the plot 
```{r}
hist(sumofStepsNA,xlab="sum of steps taken per day",main = "TOTAL STEPS",breaks=20)
```

we see that chaning and inputing missing data could have a greta impact on value of mean and media!


## Are there differences in activity patterns between weekdays and weekends?
